---
title: "R project cycle"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    css: doc.css
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE,
                      warning = FALSE)
```

# 1) <i>roxygen2</i> documentation guidelines

<ol>
<li><b> install.packages("roxygen2") </b></li>
<li> Before a function use :
<ul>
#' @title function_name
<br>#' @description function_description
<br>#' @param param_name param_format
<br>#' @return function_result
<br>#' @examples function_in_action
<br>#' @export
</ul>
<li>If in a R project and not in a R package then use the function <b>monygenise()</b> to generate the documentation</li>
</ol>

```{r}
moxygenise <- function(codepath, manpath) {
  
  apply_at_level <- function(l, f, n, ...) {
    ## function to apply a function at specified level of a nested list
    if (n < 0) {
      stop("Invalid parameter - n should be integer >= 0 -- APPLY_AT_LEVEL")
    } else if (n==0) {
      return(l)
    } else if (n == 1) {
      return(lapply(l, f, ...))
    } else {
      return(lapply(l, function(x) {apply_at_level(x, f, n-1)}))
    }
  }
  
  list.files.paths <- function(path, pattern) {
    ## function to list absolute path of all files under specified path matching certain pattern
    path <- normalizePath(path)
    return(file.path(path, list.files(path=path, pattern=pattern)))
  }
  
  sourcefiles <- list.files.paths(codepath, "\\.R$")
  source_envs <- lapply(sourcefiles, roxygen2::env_file)
  rd_blockss <- mapply(roxygen2::parse_file, sourcefiles, source_envs)
  
  help_topicss <- mapply(function(rdblock, sourceenv, sourcefile) {
    return(roxygen2::roclet_process(
      roxygen2::rd_roclet(), 
      rdblock, sourceenv, 
      dirname(sourcefile)))},
    rd_blockss, source_envs, sourcefiles)
  
  rd_codes <- purrr::flatten(apply_at_level(help_topicss, format, 2))
  
  mapply(function(text, topic, outpath=manpath) {
    cat("Write", topic, "to", outpath, "\n")
    write(text, file=file.path(outpath, topic))
  }, rd_codes, names(rd_codes))
  return(NULL)
}
```


# 2) <i>renv</i> control dependencies

[renv package official website](https://rstudio.github.io/renv/articles/renv.html)

<ol>
<li> <b> install.packages("renv") </b> </li>
<li> Initialize a new project-local environment with private R library : <b> renv::init() </b> </li>
<li> Capture all packages installed in the project library : <b>renv::settings$snapshot.type("all") </b></li>
<li> Save the state of the project in renv.lock file : <b>renv::snapshot() </b></li>
<li> To restore the state of the project as encoded in renv.lock file : <b>renv::restore() </b></li>
</ol>

# 3) CI/CD pipelines for automatic deployement

In git bash : cd project_folder_path
In Rstudio : open project

<ol>
<li> <b>git init</b> </li>
<li> Check remote repo name and address: <b>git remote -v </b>
<ul>
<li> Add new remote repo : <b>git remote add repo_name https</b></li>
<li> Add remote repo to push only : <b> git remote set-url --add --push repo_name https </b></li>
<li> Show remote repo : <b>git remote show origin</b></li>
<li> Remove remote repo : <b> git remote remove repo_name</b></li>
</ul>
</li>
<li> Check remote repo branch : <b>git branch</b>
<ul>
<li> If no branch exist : <b>git checkout -b branch_name</b></li>
<li> If want to switch branch : <b>git switch -c branch_name</b></li>
</ul>
</li>
<li> Check change in files : <b>git status</b></li>
<li> Add changes :
<ul>
<li> Stage all changes (add,delete,modify) : <b>git add -A </b></li>
<li> Stage (modify,delete) changes but not new files : <b>git add -u</b></li>
<li> Stage (add,modify) but not deletion : <b>git add .</b></li>
</ul>
</li>
<li> Remove file or folder : <b>git rm -r (--cached) folder_name</b></li>
<li> Check committed changes : <b> git status</b></li>
<li> Commit to local repo : <b> git commit -m "commit_message"</b></li>
<li> Push changes to remote repo : <b> git push repo_name branch_name </b>
<ul><li> Force the push : <b> git push -f repo_name branch_name</b></li></ul>
</li>
<li> Pull : <b>git pull (--allow-unrelated-histories) repo_name branch_name </b></li>
</ol>

# 4) Use python in R

[Support Rstudio website](https://support.rstudio.com/hc/en-us/articles/360023654474-Installing-and-Configuring-Python-with-RStudio)

<ol>
<li> Go to python shell prompt/double click pip file in Python folder </li>
<li> Ensure that your installation of python has the virtualenv package installed : pip install virtualenv </li>
<li> Create a python environment in your project :
<ol><li> cd (/d if disk change) path_to_project_dir</li>
<li> virtualenv env_name</li></ol></li>
<li> Activate your python environment : <b>env_name\\Scripts\\activate</b></li>
<li> Check the correct version of Python is activated : where python </li>
<li> Install python package in environement : pip install package_name</li>
<li> Go to RStudio IDE + open project </li>
<li> Install reticulate package : install.packages("reticulate") </li>
<li> Configure reticulate to point to Python executable in the virtualenv : Sys.setenv(RETICULATE_PYTHON = "env_name/Scripts/python")</li>
<li> Restart R session </li>
<li> Check reticulate is configured for the correct version of python : reticulate::py_config() </li>
</ol>

